---
title: "Boot Strapping"
author: "Kristal Quispe"
date: "11/25/2019"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(p8105.datasets)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
set.seed(1)
```


## Pull ourselves up by the bootstraps


```{r}
set.seed(1)
n_samp = 250
sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )
sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)
```


Show my datasets

```{r}
sim_df = 
  bind_rows(const = sim_df_const, nonconst = sim_df_nonconst, .id = "data_source") 

sim_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm") +
  facet_grid(~data_source) 
```

Fit two models ...

```{r}
sim_df_const %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy()

sim_df_nonconst %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy()
```


## how can i bootstrap

write a function to draw a bootstrap sample based on a dataframe.

```{r}
boot_sample = function(df) {
  sample_frac(df, size = 1, replace = TRUE)
}
#replace alows ppl to counted in the sample twice or more, size is expressed in proportion, here 1 is max, keep size as 1 for bootstrapping
```

```{r}
boot_sample(df = sim_df_nonconst) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5)
```

Organize a dataframe ...

```{r}
boot_straps = 
  tibble(
    strap_num = 1:1000,
    strap_sample = rerun(1000, boot_sample(df = sim_df_nonconst))
  )
```

Do some kind of analysis....

```{r}
#take of your boot straps model , fit a lim model, then look at slope
bootstrap_results = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(y ~ x, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(-strap_sample, -models) %>% 
  unnest(results)
```

summarize these results 

```{r}
bootstrap_results %>% 
  group_by(term) %>% 
  summarize(se = sd(estimate))

#how much variability in ur estimates
```


## Try the modelr package

```{r}
boot_straps = 
  sim_df_nonconst %>% 
  modelr::bootstrap(1000)
```


COPY AND PASTE!!!

```{r}
sim_df_nonconst %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(y ~ x, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```


## What if your assumptions aren't wrong?


```{r}
sim_df_const %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy()

sim_df_const %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(y ~ x, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```
# if your assumptions are correct you should get a estimate of b0 and b1

## Revisit Airbnb

```{r}
data("nyc_airbnb")
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) +
  geom_point()
```


Re-use the stuff I just did ...

```{r}
airbnb_results = 
  nyc_airbnb %>%
  filter(boro == "Manhattan") %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(price ~ stars, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(results) %>% 
  unnest(results)
```

Make a plot of the `stars` distribution.

```{r}
airbnb_results %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) + 
  geom_density()
```